Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-08-05 Paper/Manuscript_Stats&Comp/reply_letter_2nd_STCO.tex
Small edits in reply letter

@@

\noindent \hdashrule{12.5cm}{0.2pt}{2mm 1pt}

@@

\item We have updated the appearance of Figures 1, 2, 3, 4, and 5 (old numbering) in order to make them more compact and thus the overall appearance of the paper more pleasing. The new numbering corresponding to those figures is now Fig. 1, 2, 3, and 4.

@@

Figure 6 may look a bit fuzzy, but it is actually a visual effect because the curves were constructed for discrete values of the number of basis functions $m$ (Y-axis), which makes them look like stair-shaped curves when plotted, and its appearance can be confused with a blurred image. We think the resolution of the figure itself is sufficient. We have increased the size of the figures in Table 1 and have checked and updated the other figures as we saw fit.

@@

Based on the evidence that we have at this point, we can unfortunately not give evidence-based suggestions as to when to stop pre-convergence and try something else because we have seen only very few iterations to be required in all the investigated cases. With regard to high-dimensional cases, the main problem would not be more iterations (as far as we have seen) but the computational cost of each iteration. More concretely, as we discuss in detail in the paper, the more input dimensions ($D$) we have, the number of required multivariate basis functions increases ($m^*=nm^D$, with $n$=number of points and $m$=number of univariate basis functions), which affects the HMC sampling of a model fit (per iteration), but not (in a relevant manner) the number of iterations required to complete the diagnostic procedure. We have now clarified these points at the end of Section 4.5.1.

@@

We are not sure whether we can convince you of the sensibility and sufficiency of the focus of our paper that we have chosen. But what we can say is that based on the informal feedback from the community we have recieved so far, the other reviewers' and also the editor's comments, as well as over 20 citation of the corresponding preprint already, a lot of people see value in our work and its existing focus. There is certainly a lot of value in comparing HSGPs with competing methods other than exact GPs, but we do not see a way to make this part of the current paper, not only in terms of paper space, but also in terms of time, personnel, and monetary resources we currently have available to work on this topic.

@@

We apologize for creating confusion with our notation here. {\color{blue}The diagnostic Figure 5 and equations (19-24) work with a normalized lengthscale, i.e., a lengthscale $\ell$ normalized by the zero-mean, symmetric interval $S$ which contains the inpus values $x_i$ ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. In concrete in step A.1 in Section 4.5.1 we recommend values for a first guess of the lengthscale based on the normalized lengthscale. We have now clarified the role and use of the normalized lengthscale relative to $S$ throughout the paper.}

@@

Thank you for also your comment about the $\ell_i$ notation in Section 4.5.1, where $i$ is the subscript for the diagnostic iteration, conflicting with the $\ell_i$ notation used in the article where $i$ is the subscript for dimensions. Therefore, we have changed the notation in Section 4.5.1 from $\ell_i$ to $\ell^{(k)}$ to clearly differentiate it from the notation in the rest of the article where subscripts refer to dimensions.

>>>>

\section*{\normalsize Reply to reviewer comments for \\ \Large`Practical Hilbert space approximate Bayesian Gaussian processes \\ for probabilistic programming'}

@@

\noindent \hdashrule{\textwidth}{0.2pt}{2mm 1pt}

@@

\item We have updated the appearance of Figures~1, 2, 3, 4, and 5 (old numbering) in order to make them more compact and thus the overall appearance of the paper more pleasing. The new numbering corresponding to those figures is now Fig.~1, 2, 3, and 4.

@@

Figure 6 may look a bit fuzzy, but it is actually a visual effect because the curves were constructed for discrete values of the number of basis functions $m$ ($y$-axis), which makes them look like stair-shaped curves when plotted, and its appearance can be confused with a blurred image. We think the resolution of the figure itself is sufficient. We have increased the size of the figures in Table 1 and have checked and updated the other figures as we saw fit.

@@

Based on the evidence that we have at this point, we can unfortunately not give evidence-based suggestions as to when to stop pre-convergence and try something else because we have seen only very few iterations to be required in all the investigated cases. With regard to high-dimensional cases, the main problem would not be more iterations (as far as we have seen) but the computational cost of each iteration. More concretely, as we discuss in detail in the paper, the more input dimensions ($D$) we have, the number of required multivariate basis functions increases ($m^*=nm^D$, with $n$ = number of points and $m$ = number of univariate basis functions), which affects the HMC sampling of a model fit (per iteration), but not (in a relevant manner) the number of iterations required to complete the diagnostic procedure. We have now clarified these points at the end of Section~4.5.1.

@@

We are not sure whether we can convince you of the sensibility and sufficiency of the focus of our paper that we have chosen. But what we can say is that based on the informal feedback from the community we have received so far, the other reviewers' and also the editor's comments, as well as over 20 citation of the corresponding preprint already, a lot of people see value in our work and its existing focus. There is certainly a lot of value in comparing HSGPs with competing methods other than exact GPs, but we do not see a way to make this part of the current paper, not only in terms of paper space, but also in terms of time, personnel, and monetary resources we currently have available to work on this topic.

@@

We apologize for creating confusion with our notation here. {\color{blue}The diagnostic Figure~5 and equations (19--24) work with a normalized lengthscale, i.e., a lengthscale $\ell$ normalized by the zero-mean, symmetric interval $S$ which contains the inpus values $x_i$ ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. In concrete in step A.1 in Section 4.5.1 we recommend values for a first guess of the lengthscale based on the normalized lengthscale. We have now clarified the role and use of the normalized lengthscale relative to $S$ throughout the paper.}

@@

Thank you for also your comment about the $\ell_i$ notation in Section~4.5.1, where $i$ is the subscript for the diagnostic iteration, conflicting with the $\ell_i$ notation used in the article where $i$ is the subscript for dimensions. Therefore, we have changed the notation in Section~4.5.1 from $\ell_i$ to $\ell^{(k)}$ to clearly differentiate it from the notation in the rest of the article where subscripts refer to dimensions.
